Modelling Structured Societies: a Multi-relational Approach to Context Permeability

### 2015-06-28 doc/main.tex
Affiliation Corrected

		\address[ul]{Group of Studies in Social Simulation (GUESS), Laboratory of Agent Modelling, Faculdade de Ciências, Universidade de Lisboa, 1749-016 Lisboa, Portugal}
		\title{Modelling Structured Societies: a Multi-relational Approach to Context Permeability}

@@

      \section*{Acknowledgements}
      \noindent This work was supported by the Funda\c{c}\~ao para a Ci\^encia e a Tecnologia under
      the grant SFRH / BD / 86034 / 2012.

>>>>

		\address[ul]{GUESS/BioISI - Instituto de Biosistemas e Ciências Integrativas,
                  Faculdade de Ciências, Universidade de Lisboa, 1749-016 Lisboa, Portugal.}
                \title{Modelling Structured Societies: a Multi-relational Approach to Context
                  Permeability}

@@

      \section*{Acknowledgements}
      \noindent Work supported by the Funda\c{c}\~ao para a Ci\^encia e a Tecnologia under the grant
      SFRH/BD/86034/2012 and by centre grant (to BioISI, Centre Reference:
      UID/MULTI/04046/2013), from FCT/MCTES/PIDDAC, Portugal
